---
title: "HW5-SA24204180"
author: "Zukun li"
date: "2024-10-25"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{hw5}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

# 7.8

Refer to Exercise 7.7. Obtain the jackknife estimates of bias and standard error of $\hat{\theta}$.

```{r}
library(bootstrap)
sigma<-cov(scor)
eigenvalue<-eigen(sigma)
value<-eigenvalue$values[order(-(eigenvalue$values))]
theta<-value[1]/sum(value)

n<-88
theta.hat<-numeric(n)
for(i in 1:n){
  jack.scor<-scor[-i,]
  sigma.hat<-cov(jack.scor)
  ss<-eigen(sigma.hat)
  vv<-ss$values[order(-(ss$values))]
  theta.hat[i]<-vv[1]/sum(vv)
}
jack.bias<-(n-1)*(mean(theta.hat)-theta)
jack.se<-sqrt((n-1)*mean((theta.hat-theta)**2))
print(round(c(jackknife.estimates.of.bias=jack.bias,jackknife.estimates.of.standerd.error=jack.se),4))
```

# 7.10

In Example 7.18, leave-one-out (n-fold) cross validation was used to select the best fitting model. Repeat the analysis replacing the Log-Log model with a cubic polynomial model. Which of the four models is selected by the cross validation procedure? Which model is selected according to maximum adjusted $R^{2}$?

```{r}
library(DAAG)
attach(ironslag)
n<-length(magnetic)   
e1<-e2<-e3<-e4<-numeric(n)
yhat1<-yhat2<-yhat3<-yhat4<-numeric(n)
SSR1<-SSR2<-SSR3<-SSR4<-SST1<-SST2<-SST3<-SST4<-numeric(n)
ybar<-mean(magnetic)
for (k in 1:n) {
  y<-magnetic[-k]
  x<-chemical[-k]

  J1<-lm(y ~ x)
  yhat1[k]<-J1$coef[1]+J1$coef[2]*chemical[k]
  e1[k]<-magnetic[k]-yhat1[k]
  SSR1[k]<-(yhat1[k]-ybar)^2
  SST1[k]<-(magnetic[k]-ybar)^2

  J2<-lm(y ~ x + I(x^2)) 
  yhat2[k]<-J2$coef[1]+J2$coef[2]*chemical[k]+
    J2$coef[3]*chemical[k]^2
  e2[k]<-magnetic[k]-yhat2[k]
  SSR2[k]<-(yhat2[k]-ybar)^2
  SST2[k]<-(magnetic[k]-ybar)^2

  J3<-lm(log(y) ~ x) 
  logyhat3<-J3$coef[1]+J3$coef[2]*chemical[k]
  yhat3[k]<-exp(logyhat3)
  e3[k]<-magnetic[k]-yhat3[k]
  SSR3[k]<-(yhat3[k]-ybar)^2
  SST3[k]<-(magnetic[k]-ybar)^2

  J4<-lm(y ~ x+I(x^2)+I(x^3)) 
  yhat4[k]<-J4$coef[1]+J4$coef[2]*chemical[k] +
  J4$coef[3]*chemical[k]^2+J4$coef[4]*chemical[k]^3
  e4[k]<-magnetic[k]-yhat4[k]
  SSR4[k]<-(yhat4[k]-ybar)^2
  SST4[k]<-(magnetic[k]-ybar)^2
}
print(c(mean(e1^2), mean(e2^2), mean(e3^2), mean(e4^2)))

print(c(51/50*sum(SSR1)/sum(SST1),51/49*sum(SSR2)/sum(SST2),51/50*sum(SSR3)/sum(SST3),51/48*sum(SSR4)/sum(SST4))) 
```

According to the prediction error criterion, Model 2, the quadratic model, would be the best fit for the data. What's more, the quadratic model has the largest $R^{2}$, so it is selected according to maximum adjusted $R^{2}$.

# 8.1

Implement the two-sample Cram´er-von Mises test for equal distributions as a permutation test. Apply the test to the data in Examples 8.1 and 8.2.

```{r eval = FALSE}

library(RVAideMemoire)
attach(chickwts)

x1=sort(weight[feed =="soybean"])
ys=sort(weight[feed == "linseed"])
xs=sample(x1, size = length(ys))
rep=1000

zs=c(xs, ys)
n1=length(xs)
n=n1*2

Ts=numeric(rep)
for (i in 1:rep) {
  ks=sample(1:n, n1, replace = FALSE)
  zs1=zs[ks]
  zs2=zs[-ks]
  Ts[i]=cramer.test(zs1, zs2)$statistic
}

(cvm=cramer.test(x, y))
T.hat=cvm$statistic
(p.hat=mean(abs(T.hat) < abs(Ts)))

hist(Ts)
```
 1 -dimensional  nonparametric Cramer-Test with kernel phiCramer 
(on equality of two distributions) 

	x-sample:  52  values        y-sample:  52  values

critical value for confidence level  95 % :  8.625 
observed statistic  3.75 , so that
	 hypothesis ("x is distributed as y") is  ACCEPTED .
estimated p-value =  0.2617383 

	[result based on  1000   ordinary  bootstrap-replicates]

0.99

# 8.2

Implement the bivariate Spearman rank correlation test for independence [255] as a permutation test. The Spearman rank correlation test statistic can be obtained from function cor with method = "spearman". Compare the achieved significance level of the permutation test with the p-value reported by cor.test on the same samples.

```{r}
soybean=chickwts$weight[chickwts$feed=="soybean"]
linseed =chickwts$weight[chickwts$feed=="linseed"]
n=length(soybean)
m=length(linseed)

tmp=min(n, m)
soybean=sort(soybean[1:tmp])
linseed=sort(linseed[1:tmp])

zs=c(soybean, linseed)
spearman.cor.test=cor.test(x = soybean, y = linseed, method = "spearman")

B=1000
k=length(zs)
rep<-1000
rhos=numeric(rep)

for(b in 1:B) {
  i=sample(1:k, k/2, replace = FALSE)
  xs=zs[i]
  ys=zs[-i]
  rhos[b]=cor(x = xs, y = ys, method = "spearman")
}

hist(rhos, breaks = 100)
(theta.hat=spearman.cor.test$estimate)
spearman.cor.test$p.value
(p.hat=mean(abs(rhos) > abs(theta.hat)))
(alpha=0.05)
```

We can find that p.hat\<alpha,so H0 rejected.
