---
title: "hw6"
author: "Zukun Li"
date: "2024-11-01"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{hw6}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## 9.3

Use the Metropolis-Hastings sampler to generate random variables from a standard Cauchy distribution. Discard the first 1000 of the chain, and compare the deciles of the generated observations with the deciles of the standard Cauchy distribution (see qcauchyor qt with df=1). Recall that a Cauchy(θ,η) distribution has density function

$$
f(x)=\frac{1}{\theta\pi(1+[(x-\eta)/\theta]^{2})}
$$

The standard Cauchy has the Cauchy(θ =1,η= 0) density. (Note that the standard Cauchy density is equal to the Student t density with one degree of freedom.)

```{r}
set.seed(111)
theta=1
eta=0


f<-function(x){
  stopifnot(theta > 0)
  return(1/(theta*pi*(1+((x-eta)/theta)**2)))
}

m<-1e4
k<-0
u<-runif(m)
x<-numeric(m)

x[1]<-rnorm(1,mean = 1)
for(i in 2:m){
  xt<-x[i-1]
  y<-rnorm(1,mean = xt)
  r=f(y)*dnorm(x=xt,mean=y)/(f(xt)*dnorm(x=y,mean = xt))
  if(u[i]<=r){
    x[i]=y
  }else{
    k=k+1
    x[i]=xt
  }
}
is = 5001:5500
par(mfrow = c(1,2))
plot(is, x[is], type="l")
a<-ppoints(100)
QR<-tan(pi*(a-0.5))
Q<-quantile(x, a)
qqplot(QR, Q, main="",
        xlab="Cauty Quantiles", ylab="Sample Quantiles")
abline(0,1,col='blue',lwd=2)
hist(x, probability = TRUE, breaks = 100)
plot.x = seq(min(x), max(x), 0.01)
lines(plot.x, f(plot.x))
par(mfrow = c(1,1))
```

## 9.8

This example appears in [40]. Consider the bivariate density

$$
f(x,y) \propto \binom{n}{x}y^{x+a-1}(1-y)^{n-x+b-1},\ x=0,1,...,n,0\le y\le 1
$$

It can be shown (see e.g. [23]) that for fixed a,b,n, the conditional distributions are Binomial(n,y)andBeta(x+a,n−x+b). Use the Gibbs sampler to generate a chain with target joint density f(x,y).

```{r}
n<-100
a<-20
b<-30
f=function(x,y){
  return(factorial(n)/(factorial(x)*factorial(n-x))*(y**(x+a-1))*((1-y)**(n-x+b+1)))
}
m<-5000
X=matrix(0,nrow = m,ncol = 2)
for(i in 2:m){
  xt=X[i-1,]
  xt[1]=rbinom(1,n,xt[2])
  xt[2]=rbeta(1,xt[1]+a,n-xt[1]+b)
  X[i,]=xt
}
x<-X[1001:m,]
cat('Means: ',round(colMeans(x),2))
cat('Standard errors: ',round(apply(x,2,sd),2))
cat('Correlation coefficients: ', round(cor(x[,1],x[,2]),2))

plot(x[,1],type='l',col=1,lwd=2,xlab='Index',ylab='Random numbers')
lines(x[,2],col=2,lwd=2)
legend('bottomright',c(expression(X[1]),expression(X[2])),col=1:2,lwd=2)
```
