---
title: "hw8"
author: "Zukun Li"
date: "2024-11-14"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{hw8}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## 11.7

Use the simplex algorithm to solve the following problem. Minimize 4x +2y +9z subject to $$
\begin{aligned}
2x+y+z&\le 2\\
x-y+3z&\le3\\
x\ge0,y\ge0,z&\ge0
\end{aligned}
$$

```{r,warning=FALSE}
library(lpSolve)

objective <- c(4, 2, 9)

constraints <- matrix(c(2, 1, 1,
                        1, -1, 3), 
                      nrow = 2, byrow = TRUE)

rhs <- c(2, 3)

direction <- c("<=", "<=")

solution <- lp("min", objective, constraints, direction, rhs, compute.sens = TRUE)

cat("Optimal value:", solution$objval, "\n")
cat("Optimal solution (x, y, z):", solution$solution, "\n")

```

# 11.1

## 3

Use both for loops and lapply() to fit linear models to the mtcars using the formulas stored in this list:

formulas \<- list( mpg \~ disp, mpg \~ I(1 / disp), mpg \~ disp + wt, mpg \~ I(1 / disp) + wt )

```{r}
formulas <- list(
 mpg ~ disp,
 mpg ~ I(1 / disp),
 mpg ~ disp + wt,
 mpg ~ I(1 / disp) + wt
 )

v1<-vector("list",4)
for (i in 1:4){
v1[i] <- lapply(i,function(i) {lm(formulas[[i]], data = mtcars)})
}
```

## 4

Fit the model mpg \~ disp to each of the bootstrap replicates of mtcars in the list below by using a for loop and lapply(). Can you do it without an anonymous function

bootstraps \<- lapply(1:10, function(i) { rows \<- sample(1:nrow(mtcars), rep = TRUE) mtcars[rows, ] })

```{r}
bootstraps <- lapply(1:10, function(i) {
 rows <- sample(1:nrow(mtcars), rep = TRUE)
 mtcars[rows, ]
})

v2<-vector("list",10)
for (i in 1:10){
v2[i] <- lapply(bootstraps[i], lm, formula = mpg ~ disp)
}
```

## 5

For each model in the previous two exercises, extract $R^{2}$ using the function below. rsq \<- function(mod) summary(mod)\$r.squared

```{r}
rsq <- function(mod) summary(mod)$r.squared
# question 3
sapply(v1, rsq)
#question 4
sapply(v2, rsq)
```

# 11.2

## 3

The following code simulates the performance of a t-test for non-normal data. Use sapply() and an anonymous function to extract the p-value from every trial.

trials \<- replicate( 100, t.test(rpois(10, 10), rpois(7, 10)), simplify = FALSE ) Extra challenge: get rid of the anonymous function by using [[ directly.

```{r}
trials <- replicate(
         100,
         t.test(rpois(10, 10), rpois(7, 10)),
         simplify = FALSE
       )
sapply(trials, function(x) x[["p.value"]])
sapply(trials, "[[", "p.value")
```

## 6

Implement a combination of Map() and vapply() to create a lapply() variant that iterates in parallel over all of its inputs and stores its outputs in a vector (or a matrix). What arguments should the function take?

# 17.5

## 4

Make a faster version of chisq.test() that only computes the chi-square test statistic when the input is two numeric vectors with no missing values. You can try simplifying chisq.test() or by coding from the mathematical definition.

```{r}
chisq_test_fast <- function(x, y) {
  if (!is.numeric(x) || !is.numeric(y)) {
    stop("Both inputs must be numeric vectors")
  }
  if (any(is.na(x)) || any(is.na(y))) {
    stop("Input vectors must not contain missing values")
  }
  n <- rbind(x, y)
  n1 <- rowSums(n)
  n2 <- colSums(n)
  k <- sum(n)
  m <- tcrossprod(n1,n2) / k

  x_stat <- sum((n - m)^2 / m)
  df <- (length(n1) - 1) * (length(n2) - 1)
  p.value <- pchisq(x_stat, df = df, lower.tail = FALSE)

  list(x_stat = x_stat, df = df, p.value = p.value)
}
```

## 5

Can you make a faster version of table() for the case of an input of two integer vectors with no missing values? Can you use it to speed up your chi-square test?

```{r}
library(fastmatch)
fast_table <- function(x, y) {
  if (!is.integer(x)) x <- as.integer(x)
  if (!is.integer(y)) y <- as.integer(y)
  
  a_sort <- sort(unique(a))
  b_ssort <- sort(unique(b))
  
  a_len <- length(a_sort)
  b_len <- length(b_sort)
  
  dim <- c(a_len, b_len)
  pr <- a_len * b_len
  dn <- list(a = a_sort, b = b_sort)
  
  bin <- fmatch(a, a_sort) + a_len * fmatch(b, b_sort) - a_len
  y <- tabulate(bin, pr)
  
  y <- array(y, dim = dim, dimnames = dn)
  class(y) <- "table"
  
  y
}
```
