---
title: "hw2"
author: "Zukun li"
date: "2024-10-04"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{hw2}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## Question 5.4

Write a function to compute a Monte Carlo estimate of the Beta(3,3) cdf,and use the function to estimate $F(x)$ for $x=0.1,0.2,...,0.9$.Compare the estimates with the values returned by the $pbeta$ function in R.

## Answer

As $F(x)=\int_{-\infty}^{x}f(x)dx$ In this question,

$$\begin{align}
F(x) = &\int_{0}^{x}f(x;\alpha,\beta)dx\\
=& \int_{0}^{x}beta(x;3,3)dx\\
=&\int_{0}^{x}\frac{1}{B(3,3)}x^{3-1}(1-x)^{3-1}dxB\\
\end{align}
$$ We use Monte Carlo estimator: $$\begin{align}
&F(x) = E_{x}(\frac{1}{x\times b(3,3)}t^{2}(1-t)^{2})dt\\
&x\sim U(0,1)\\
&Its estimate:\hat{\theta}=\frac{1}{m}\sum_{i=1}^{m}\frac{1}{x\times b(3,3)}t_{i}^{2}(1-t_{i})^{2}
\end{align}
$$

```{r}
n=10000
Beta.cdf = function(x){
  y=runif(n)
  return(mean(dbeta(x*y,3,3))*x)
}
t<-seq(0.1,0.9,0.1)
x1<-sapply(t,function(t) pbeta(t,3,3))
x2<-sapply(t,function(t) Beta.cdf(t))
round(rbind(x1,x2),4)
```

## Question 5.9

The Rayleigh density is $$\\f(x)=\frac{x}{\sigma^{2}}e^{-x^{2}/(2\sigma^{2})},x\geq0,\sigma>0$$ Implement a function to generate samples from a Rayleigh($\sigma$)distribution, using antithetic variables.What is the percent reduction in variance of $\frac{X+X^{'}}{2}$compared with $\frac{X_{1}+X_{2}}{2}$for independent$X_{1},X_{2}$?

## Answer

Make $$\begin{align}
&u=1-e^{-\frac{x^{2}}{2\sigma^{2}}}\\
&u^{'}=1-u=e^{-\frac{x^{2}}{2\sigma^{2}}}\\
we\ get\  &u\sim U(0,1)\\
&x=\sigma\sqrt{-2ln(1-u)}\\
and\ &x^{'}=\sigma\sqrt{-2ln(u)}
\end{align}
$$ So we get the function below which can generate samples from a Rayleigh($\sigma$)distribution,using antithetic variables:

```{r}
n=10000
a = 2#value of σ
pdf1.Rayleigh = function(x){
  u1=runif(n/2)
  return(a*(-2*log(1-u1))**0.5)
}
pdf2.Rayleigh = function(x){
  u2=runif(n/2)
  return(a*(-2*log(u2))**0.5)
}
```

$$\begin{align}
as\ E(X)&=\int_{0}^{\infty}\frac{x^{2}}{\sigma^{2}}e^{-\frac{x^{2}}{2\sigma^{2}}}dx\\
&=\sqrt{\frac{\pi}{2}}\sigma\\
and\ Var(x)&=E(X^{2})-(E(X))^{2}\\
&=\int_{0}^{\infty}\frac{x^{3}}{\sigma^{2}}e^{-\frac{x^{2}}{2\sigma^{2}}}dx-\frac{\pi}{2}\sigma^{2}\\
&=(2-\frac{\pi}{2})\sigma^{2}\\
we\ can\ get\ \ Var(\frac{X_{1}+X_{2}}{2})&=(1-\frac{\pi}{4})\sigma^{2}\approx0.2146\sigma^{2}\\
and \ Var(\frac{X+X^{'}}{2})&=(1-\frac{\pi}{4})\sigma^{2}+\frac{Cov(X,X^{'})}{2}\\
because\ X&=\sigma\sqrt{-2ln(1-u)}\\
and\ X^{'}&=\sigma\sqrt{-2ln(u)}\ (u\sim U(0,1))\\
so\ Cov(X,X^{'})&=E(XX^{'})-E(X)E(X^{'})\\
&=\int_{0}^{1}2\sigma^{2}\sqrt{ln(x)ln(1-x)}dx-\frac{\pi}{2}\sigma^{2}\\
&\approx-0.4065\sigma^{2}\\
then\ Var(\frac{X+X^{'}}{2})&\approx0.0114\sigma^{2}\\
finally,we\ find\ the\ percent\\
reduction\ in\ varience\ is\ about:\\
&94.7\%
\end{align}
$$

## Question 5.13

Find two importance functions $f_{1}$and$f_{2}$that are supported on$(1,\infty)$and are 'closed' to $$g(x)=\frac{x^{2}}{\sqrt{2\pi}}e^{-x^{2}/2}\   \ x>1.
$$ Which of your two importance functions should produce the smaller variance in estimating $$\int_{1}^{\infty}\frac{x^{2}}{\sqrt{2\pi}}e^{-x^{2}/2}dx
$$ by importance sampling?Explain.

## Answer

```{r}
g = function (x) {
  x^2/sqrt(2*pi)*exp(-x^2/2)
}
x = seq(0,10,0.1)
y = g(x)
plot(x,y,type="l")

```

The probability distribution of the function is mainly concentrated in (1,4) Derive the function,we get:

$$
\frac{\partial g(x)}{\partial x}=\frac{1}{\sqrt{2\pi}}(2x-x^{3})e^{-\frac{x^{2}}{2}}=0\\
we\ find\ when\ x=\sqrt{2}\\
g(x)\ get\ the\ maximum\ value\sqrt{\frac{2}{\pi}}e^{-1}
$$ so,we choose the importance function $f_{1}\sim N(1.5,1)$and $f_{2}\sim Weibull(2,2)$

```{r}
g = function (x) {
  x^2/sqrt(2*pi)*exp(-x^2/2)
}
x = seq(1,10,0.1)
y = g(x)
plot(x,y,type="l",ylim=c(0,1))
y_norm<-dnorm(x,mean = 1.5, sd= 1)
y_weibull<-dweibull(x,shape = 2,scale = 2)
lines(x,y_norm,col="red",ylim=c(0,1))
lines(x,y_weibull,col="blue",ylim=c(0,1))
sd_norm<-sd(y/y_norm)
sd_weibull<-sd(y/y_weibull)
rbind(sd_norm,sd_weibull)
```

so ,the weibull distribution is better

## Question: Fast Sort

For $n=10^{4},2*10^{4},4*10^{4},6*10^{4},8*10^{4}$,apply the fast sorting algorithm to randomly permuted numbers of 1,...,n. Calculate computation time averaged over 100 simulations,denoted by$a_{n}$. Regress $a_{n}\ on\ t_{n}:=nlog(n)$,and graphically show the results(scatter plot and regression line).

## Answer

```{r chunk-name, eval=FALSE, echo=TRUE,results='asis'}
n=10000
t<-c(n,2*n,4*n,6*n,8*n)

##快速排序算法
quicksort=function(x){
    if(length(x)<=1)return(x)
    x0<-x[1]
    loc<-1
    low<-1
    n<-length(x)
    high<-n
    while(low!=high){
        if(loc==low){
            if(x[high]<x[loc]){
                tmp<-x[high]
                x[high]<-x[loc]
                x[loc]<-tmp
                low=low+1
                loc=high
            }else{
                    high=high-1
                }
            }else{
                if(x[low]>x[loc]){
                    tmp<-x[low]
                    x[low]<-x[loc]
                    x[loc]<-tmp
                    high=high-1
                    loc=low
                }else{
                    low=low+1
                }
           }
        }
    L=c()
    R=c()
    if(low>1) L=x[1:(low-1)]
    if(low<length(x)) R=x[(low+1):n]
    return(c(quicksort(L),x[low],quicksort(R)))
}

time<-numeric(5)
k<-0
for(i in t){
  k<-k+1
  random_sample=sample(1:n,i,replace=TRUE)
  x<-numeric(100)
  for(j in 1:100){
    start<-Sys.time()
    y<-quicksort(random_sample)
    end<-Sys.time()
    x[j]<-(end-start)
  }
  time[k]<-mean(x)
}
##回归分析
x_log_x<-t*log(t)
model<-lm(time ~ x_log_x)
y_pred<-predict(model)
polt_data<-data.frame(x_log_x=x_log_x,y=time,y_pred=y_pred)
ggplot(plot_data,aes(x=x_log_x))+
  geom_point(aes(y=y),color="blue")+  
  geom_line(aes(y=y_pred),color="red") + 
  labs(title="Regression of y on x * log(x)",
       x="x * log(x)",
       y="y")+
  theme_minimal()
```
